Scalar on Function Regression

### 2022-01-04 Presentation/slides.tex

	\begin{frame}{Simulation Setup \& Application}
		Jona
		\begin{itemize}
			\item Compare b-spline / fourier regression chosen via criterion (cv/aic/...)
			\item Similar for fpca
			\item generate new curves from observed curves motivated by Karhunen-Loeve expansion
			\item Compare optimal variants with test and training sets
			\item Connect to Application
		\end{itemize}
	\end{frame}

>>>>

	\begin{frame}{FPCA - Plots}
		\begin{minipage}[t]{0.79\textwidth}
			\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
		\end{minipage}
		\begin{minipage}[t]{0.19\textwidth}
			Lorem Ipsum Dolor Sit Amet
		\end{minipage}
	\end{frame}

	\begin{frame}{Simulation Setup \& Application}
		\begin{itemize}
		\item
		 Use the gasoline dataset (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
		\item 
		Generate new curves from gasoline dataset, motivated by Karhunen-Loeve expansion:

		$$F^{new}(\omega)(t) = \mu^{NIR}(t) + \sum_{j = 1}^{\infty} \xi_j^{new} \nu_j(t)^{new}$$ \\
		where \\
		 \vspace{0.1cm}
		$$\xi_{j}^{new} \in  \mathcal{N}_{n}(0,\Sigma)$$ \\
		and $\nu_j(t)^{new}$ be a $grid \times n_{FPC}$ matrix.

		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
		Following Reiss and Ogden (2007), let $f_1$ and $f_2$ be two true coefficient functions that differ in smoothness: 
		\vspace{0.4cm}

   $f_1 = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
   \vspace{0.1cm}

    $	f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}$

		\end{itemize}
		\vspace{0.1cm}
		\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=3cm]{smooth_function.png}
  \captionof{figure}{$f_1$, smooth function}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=3cm]{bumpy_function.png}
  \captionof{figure}{$f_2$, bumpy function}
  \label{fig:test2}
\end{minipage}
\end{figure}

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
    		Let \\
    		 \vspace{0.1cm}

    		$Y_{1,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$, \\
    		  $Y_{2,f} = NIR \times f + \mathcal{N}(0,1) \times var(NIR \times f)/0.9 - var(NIR \times f)$ be two responses for $f \in f_1, f_2$.		
    		 	\item
    		 	 Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP,...)
			\item 
			{\color{green} add results here!}

		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
    		Use insights from the simulation study to uncover dependence.
    		\item
    		Same setup, but without generated curves.
    		\item
    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
    		\item
    		Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}
